\documentclass[10pt,twocolumn]{article}
\usepackage[a4paper,top=1cm,bottom=1cm,left=1cm,right=1cm,marginparwidth=1cm]{geometry}
\title{\textbf{Portfolio Construction\vspace{-2em}}}
\date{}
\begin{document}
\setlength{\parskip}{10px}%
\setlength{\parindent}{0pt}
\setlength{\footskip}{1.5em}
\maketitle
\begin{abstract}
{\em Abstract...}
\end{abstract}

\section{Section} %Section

\textbf{Opinion:} Altcoin doesn't make sense in current market. It is no longer
like years ago where there's only Bitcoin and other coins, now there's main
sectors that do different things. Digital assets. 

\section{Types of digital assets}

\textbf{Advice:} Cryptocurrency is one of four different digital assets. Bitcoin
falls into the cryptocurrency sector and main purpose is a store of value and
maybe a medium of exchange. Second sector is protocol and platforms, which is
currently led by Ethereum. Analogous to iOS app-store. Third type of digital
asset is asset-backed-tokens, backed by equity, debt, income-stream, or other digital
assets. Fourth type of ditial asset (potentially the most revolutionary) is
passthrough-tokens. Accrewing value and passing that value to token holders.
Binance coin is a passthrough-token.  

\textbf{Advice:} May be helpful to be diversified in all four of the sectors and
find specialization as time goes on and industry matures. 

\subsection{Interesting projects}
\textbf{CHZ:} Digitization of fan experience. Three different investments here:
Socios, CHZ token, individual fan tokens. Perfect use-case for blockchain
assets. 

\textbf{HXRO:} Gamified option trading. Passthrough-token. 

\textbf{AXS:} Axie infinity. You earn an asset in a game, can take that asset
outside the game and use in another game or sell it. Strong management team,
strong product-market fit in blockchain gaming, unique use-case of how token
integrates into the game, etc. 

\subsection{Investing}

\textbf{Advice:} Make sure to categorize assets into each of the four
categories. Find out how to value such asset. Does it have a similar real-world
existing conterpart? 

\section{Investing in DeFi and NFTs}
\subsection{DeFi}
Decentralized exchanges: Uniswap, Sushiswap, 0x. 
Lending protocals. Maker Dao, Aave, Compound. 

Risks
Lendingside: risks of using smart contracts bugs. If borrowing, margin risk. 

Insurance space: few \% a year for something that's been around for a long time
like Compound. Others are in the tens of percents. 

Decentralized exchanges: 
Bull theses: Gamestop. 

1inch
Maker Dao

\subsection{NFTs}
Opensea (EBAY): Buy and sell NFTs. 
Foundation (Curated selections)

\subsection{Interoperability}
Main layer 0s: Polkadot and Cosmos. 

--

Want exposure to layer 1s: Bitcoin and Ethereum. Defi is next big investable
sector. Buy protocals that have seen the most growth. Interoperability layers:
small amounts in Polkadot and Cosmos. Interesting: Centralized exchange tokens
like BNB. 

Time horizens. Buy and hold

\textbf{Info:} Bitcoin has reached maturity as digital gold. 

\textbf{} DeFi is still in its experimental phase. DeFi is 5-10 years away from
competing with traditional investing infrastructure. Analogous to e-commerse in
1995. It will change the future, but it's too early. 

Portfolio.  


NFTs and Gaming and Gaming NFTs are going to be good retail onramps to crypto. 

Interoperability: 
\end{document}